Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-08 Writing/manuscript_cea.rmd
test
Update figures and tables

(field_Ndesign + ggtitle("(a) Trial Design")) |
  (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
```

@@

```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
report_table_optN
# knit_print(report_table_optN)
```

@@

`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9))`

@@

`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9))`

>>>>

# (field_Ndesign + ggtitle("(a) Trial Design")) |
#   (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
field_Ndesign | vis_yield_subplot
```

@@

```{r table-optN-subplot-wide, tab.cap = "Mean RMSE of EONR (kg/ha) estimation and profit-deficit ($/ha) by ML methods and modeling scenarios"}
report_table_optN
```

@@

`r ftext('NOTE: The red line in the figures denotes the 1-to-1 line to show the ideal relationship between true and estimated treatment effects.', fp_text(font.size = 9, font.family = "Times New Roman"))`

@@

`r ftext('NOTE: The red line in the figures denotes the best-fit line to explain the relationship between the RMSEs of EONR prediction and yield prediction.', fp_text(font.size = 9, font.family = "Times New Roman"))`
